### 2014-02-18 proposal/new_proposal.tex
small edits to proposal

It has become standard practice for online retailers to recommend one or more
products to prospective customers who have viewed or purchased an item. These
recommendations are generally derived from collaborative filtering or other
data-mining techniques employed by the retailer or a third-party service
provider. Importantly, these recommendations provide a source of publicly
available business intelligence by relating the items in their catalogue.
Specifically, these online recommendations logically form a directed graph in
with the vertices are products and an edge pointing from item A to item B
indicates that customers who view or purchase item A are recommended item B.
Given the recommendation graphs of two or more distinct retailers, our goal is
to determine new, meaningful edges that connect these graphs in a way that would
allow one retailer to relate their products to those of another retailer.

@@

\subsection*{Method 1}
Create similarity scores between items. If items are similar, we add edges in
both directions to the recommendation graph. To determine the threshold of how
high the score must be before adding an edge, we calculate the average
similarity between items that are connected in the original graph.  These edges
can connect two items in the same catalogue or items across catalogues.

@@

\subsection*{Method 3}
The final method leverages both content-similarity and the structure of the
recommendation graphs. First, we combine the recommendation graphs using an
identity function and run a random-walk algorithm, as in method 2. This
determines how 'far,' in a sense, any product is from any other product. To
determine if there should be an edge added from product A to product B, we use
the content-similarity function of method 1 to compare A to every other product
in the catalogue and sum these scores up with the weights from the random-walk
originating at product B. Thus content-similarity from product A to a product
that is near product B in the recommendation graph increases the likelihood
that product A should be connected to product B. \emph{An equation would
probably be good in here}. For this method, we also add the top X edges based
on the threshold in method 1.

@@

For this experiment, we collect the top edges to be added for each of the three
methods. We show a subset of them to a number of people who rate them in
exchange for small sexual favors. The tester is asked 'How true is the
following statement: If someone likes product 1, they will probably like
product 2', followed by the pictures and descriptions of the two items of the
directed edge. The tester answers on a 5 point scale and the results are
aggregated. Each tester is shown edges from each of three methods, to decrease
bias from a biased tester.

>>>>

It has become standard practice for online retailers to recommend one or more
products to prospective customers who have viewed or purchased an item. These
recommendations are generally derived from collaborative filtering or other
data-mining techniques employed by the retailer or a third-party service
provider. Importantly, these recommendations provide a source of publicly
available business intelligence by relating the items in their catalogue.
Specifically, these online recommendations logically form a directed graph in
which the vertices are products and an edge pointing from item A to item B
indicates that customers who view or purchase item A are recommended item B.
Given the recommendation graphs of two or more distinct retailers, our goal is
to determine new, meaningful edges that connect these graphs in a way that would
allow one retailer to relate their products to those of another retailer.

@@

\subsection*{Method 1}
For the baseline method, we create similarity scores between items based on the
given content of each item. If items are similar, we add edges in
both directions to the recommendation graph. To determine the threshold of how
high the score must be before adding an edge, we calculate the average
similarity between items that are connected in the original graph.  These edges
can connect two items in the same catalogue or items across catalogues.

@@

\subsection*{Method 3}
The final method leverages both content-similarity and the structure of the
recommendation graphs. First, we combine the recommendation graphs using an

identity function and run a random-walk algorithm, as in method 2. This
determines how 'far,' in a sense, any product is from any other product. To
determine if there should be an edge added from product A to product B, we use
the content-similarity function of method 1 to compare A to every other product
in the catalogue and sum these scores up with the weights from the random-walk
originating at product B. Thus content-similarity from product A to a product
that is near product B in the recommendation graph increases the likelihood
that product A should be connected to product B. \emph{An equation would
probably be good in here}. For this method, we also add the top X edges based
on the threshold in method 1.

@@

For this experiment, we collect the top edges to be added for each of the three
methods. We show a subset of them to a number of people who rate them subjectively. 
The tester is asked 'How true is the following statement: If someone likes
product 1, they will probably like product 2', followed by the pictures and
descriptions of the two items of the directed edge. The tester answers on a 5
point scale and the results are aggregated. Each tester is shown edges from
each of three methods, to decrease bias from a biased tester.
